A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2019-01-27 article/06_Remarks.Rmd
reorganized the technical stuff at the end

# Acknowledgements

@@

Finally I would like to thank Sergi Valverde (Pompeu Fabra University Barcelona) and Simon Carrignon (Barcelona Supercomputing Center) for the organisation of the session *Evolution of Cultural Complexity III* at the Conference on Complex Systems 2018 in Thessaloniki where this paper was initially presented.

>>>>

# Remarks

## Acknowledgements

@@

Finally I would like to thank Sergi Valverde (Pompeu Fabra University Barcelona) and Simon Carrignon (Barcelona Supercomputing Center) for the organisation of the session *Evolution of Cultural Complexity III* at the Conference on Complex Systems 2018 in Thessaloniki (Greece) where this paper was initially presented.

## Declaration of Conflicting Interests

The author declared no potential conflicts of interest with respect to the research, authorship, and/or publication of this article.

## Funding

This paper was prepared without financial support, except for a 300Euro travel grant to attend the Conference on Complex Systems 2018 by the International Center of Kiel University.
